---
title: "pokedex"
output: html_document
---

The `pokedex` package offers a suite of functions allowing a user to interact with the [PokeAPI](https://pokeapi.co/). Information about berries, evolutions, regions, and game generations is viewable.

Functions available include:

- `get_berry`  
- `evolution_tree`  
- `get_berry`
- `get_types`  
- `type_effectiveness`

### Installation

The package can be installed from GitHub using,

```
devtools::install_github("UBC-MDS/pokedex")
```

### Usage

All functions perform similarly, taking a string specifying a pokemon or berry name, type, or relationship.

For example, information about any berry can be found as follows:

```
get_berry("cheri")
```

Note that a message will be returned if the name isn't in the PokeAPI database. Berry names must be in lowercase. A dataframe of available berries can be found by loading,

```
data(berry_lookup)
```

Users can also access information about type effectiveness. If a user wanted to know which types fire is strong against, the following will return that information,

```
type_effectiveness("fire", "strong", "against")
```

Users can access the evolution tree for baby pokemon. If a user wants to know which pokemon Bulbasaur evolves into, the following will return the trigger and minimum level the user must reach to evolve:

```
evolution_tree("bulbasaur")
```

### Examples

A simple example of how to generate plots:

```{r}
# devtools::install_github("UBC-MDS/pokedex")

suppressPackageStartupMessages(library(tidyverse))
library(pokedex)

# easy to generate plots with
get_types("berry") %>% 
  map_dfr(get_berry) %>% 
  mutate(Name = forcats::fct_reorder(Name, Size)) %>% 
  ggplot() +
  geom_point(aes(x = Size, y = Name)) +
  ggtitle("BERRY SIZES")
```

Or simply get some information:

```{r}
get_types("version", limit = 25) %>% 
  map_dfr(get_region)
```

